---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

### string
This package is complementary to stringr package. It includes three functions: `string_insert`, `string_cut` and `string_replace`. `string_insert` inserts a string to another string at a given position. `string_cut` cuts a substring between two given positions from a string. `string_replace` replaces a substring between two given positions in a string with another string.

### Installation
```{r installation, eval = FALSE}
devtools::install_github("mynamedaike/string")
```

### Quick demo
Import string library
```{r}
library(string)
```

string_insert inserts a string to another string at a given position
```{r}
a <- "apple pear "
b <- "banana "
string_insert(a, b, as.integer(0))
string_insert(a, b, as.integer(6))
string_insert(a, b, as.integer(11))
```

string_cut cuts a substring between two given positions from a string
```{r}
a <- "apple banana pear "
string_cut(a, as.integer(1), as.integer(6))
string_cut(a, as.integer(7), as.integer(13))
string_cut(a, as.integer(14), as.integer(18))
```

string_replace replaces a substring between two given positions in a string with another string
```{r}
a <- "apple banana pear "
b <- "orange"
string_replace(a, b, as.integer(1), as.integer(5))
string_replace(a, b, as.integer(7), as.integer(12))
string_replace(a, b, as.integer(14), as.integer(17))
```
