---
title: "string"
author: "Ke Dai"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package is complementary to stringr package. It includes three functions: `string_insert`, `string_cut` and `string_replace`. `string_insert` inserts a string to another string at a given position. `string_cut` cuts a substring between two given positions from a string. `string_replace` replaces a substring between two given positions in a string with another string.

Import string library
```{r}
library(string)
```

`string_insert`
```{r}
a <- "apple pear "
b <- "banana "
string_insert(a, b, as.integer(0))
string_insert(a, b, as.integer(6))
string_insert(a, b, as.integer(11))
```

`string_cut`
```{r}
a <- "apple banana pear "
string_cut(a, as.integer(1), as.integer(6))
string_cut(a, as.integer(7), as.integer(13))
string_cut(a, as.integer(14), as.integer(18))
```

`string_replace`
```{r}
a <- "apple banana pear "
b <- "orange"
string_replace(a, b, as.integer(1), as.integer(5))
string_replace(a, b, as.integer(7), as.integer(12))
string_replace(a, b, as.integer(14), as.integer(17))
```
